The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-02-01 Text/paper.tex
added rand findings
wrote a little section on rand findings, not sure where to put standard deviation yet.

\subsection*{Against Rand}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314

>>>>

\subsection*{Against Rand}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rand is 0.06524314. 
There are a few notable things when comparing the performance of our bots. Firstly, while both ml\_minimal and ml\_stripped performed worse that the stock ml bot, as was expected, ml\_stripped actually performs worse than ml\_minimal, despite the latter of the two having the smaller feature set. Secondly, stripping away most of the feature set in ml\_minimal only led to a relatively small performance loss. Lastly, while ml\_enriched and ml\_advanced perform, respectively, a little better and a little worse when compared to the stock ml bot, when we combined the feature sets of these two bots in ml\_combined, it led to an performance increase of almost 10\% compared to the default ml bot.
